---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![DOI](https://zenodo.org/badge/960506984.svg)](https://doi.org/10.5281/zenodo.16949291)

### *Moved to https://github.com/quest-bih/ctregistries and archived as [v1.0.1](https://github.com/quest-bih/ctregistries/releases/tag/v1.0.1)*

# ctregistries

The goal of ctregistries is to facilitate the detection and analysis of clinical trial registration numbers. ctregistries is primarily a data package of regular expressions (regexes) and provides some R functions for implementing the regexes.

Regular expressions were developed for trial registration numbers (TRN) from World Health Organization (WHO) International Clinical Trials Registry Platform (ICTRP) Primary Registries (https://www.who.int/ictrp/network/primary/en/) and MEDLINE Databank Sources (https://www.nlm.nih.gov/bsd/medline_databank_source.html).

Additional, non-trial databanks indexed by MEDLINE (e.g., figshare) are also included, without regexes.

## Installation

You can install the development version of ctregistries from GitHub:

``` r
# install.packages("devtools")
devtools::install_github("maia-sh/ctregistries")
```

## Dataset

ctregistries provides the `registries` dataframe with regular expressions for each registry. The `registries` dataframe is a subset of the larger `databanks` dataframe which additionally includes non-trial databanks indexed by MEDLINE (e.g., figshare) without regexes. `registries` is created by filtering `databanks` for `databank_type == "registry`.

```{r dataset}
library(ctregistries)

head(registries) %>% knitr::kable()

databanks$databank
```

## Functions
ctregistries provides some functions implementing the `registries` dataset to detect trial registration numbers and registries in both vectors and dataframes.

```{r example}
library(ctregistries)

# Check whether there is a TRN
has_trn(c("NCT00312962", "hello", "euctr2020-001808-42", NA))

# Extract the TRNs
which_trn("NCT00312962 and euctr2020-001808-42")
which_trns(c("NCT00312962", "hello", "euctr2020-001808-42", NA))

# Identify the registry
which_registry("NCT00312962 and euctr2020-001808-42")
which_registries(c("NCT00312962", "hello", "euctr2020-001808-42", NA))

# Add the trn and registry to a dataframe
mutate_trn_registry(sample_trn_df, text)
```


## Citation

> Salholz-Hillel M (2022). ctregistries: Data package and R functions for clinical trial registries and other MEDLINE databanks. doi:10.5281/zenodo.16949292, Version 1.0.1, [RRID:SCR_024412](https://scicrunch.org/resolver/SCR_024412), <https://github.com/maia-sh/ctregistries>.

ctregistries was initially developed for the following research
project:

> Salholz-Hillel M, Strech D, Carlisle B (2022). Results publications are inadequately linked to trial registrations: An automated pipeline and evaluation of German university medical centers. _Clinical Trials_, *19*(3), 337-346. doi:10.1177/17407745221087456.
