---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ctregistries

*In Development*

<!-- badges: start -->
<!-- badges: end -->

The goal of ctregistries is to facilitate the detection and analysis of clinical trial registration numbers. ctregistries is primarily a data package of regular expressions (regexes) and provides some R functions for implementing the regexes.

Regular expressions were developed for trial registration numbers (TRN) from World Health Organization (WHO) International Clinical Trials Registry Platform (ICTRP) Primary Registries (https://www.who.int/ictrp/network/primary/en/) and MEDLINE Databank Sources (https://www.nlm.nih.gov/bsd/medline_databank_source.html).

Additional, non-trial databanks indexed by MEDLINE (e.g., figshare) are also included, without regexes.

## Installation

You can install the development version of ctregistries from GitHub:

``` r
# install.packages("devtools")
devtools::install_github("maia-sh/ctregistries")
```

## Dataset

ctregistries provides the `registries` dataframe with regular expressions for each registry. The `registries` dataframe is a subset of the larger `databanks` dataframe which additionally includes non-trial databanks indexed by MEDLINE (e.g., figshare) without regexes. `registries` is created by filtering `databanks` for `databank_type == "registry`.

```{r dataset}
library(ctregistries)

head(registries)

databanks$databank
```

## Functions
ctregistries provides some functions implementing the `registries` dataset to detect trial registration numbers and registries in both vectors and dataframes.

```{r example}
library(ctregistries)

# Check whether there is a TRN
has_trn(c("NCT00312962", "hello", "euctr2020-001808-42", NA))

# Extract the TRNs
which_trn("NCT00312962 and euctr2020-001808-42")
which_trns(c("NCT00312962", "hello", "euctr2020-001808-42", NA))

# Identify the registry
which_registry("NCT00312962 and euctr2020-001808-42")
which_registries(c("NCT00312962", "hello", "euctr2020-001808-42", NA))

# Add the trn and registry to a dataframe
mutate_trn_registry(sample_trn_df, text)
```

## To Do
- [ ] Add checks within functions
  - [ ] Check input variable type
  - [ ] Check input (column) name conflicts (e.g., databank, trn_regex)
- [ ] Add tests: use_testthat()
- [ ] Consider removing `check_registry` since just comparing strings...
- [ ] Change license (CCBY or AGPL, unclear since partially data package)
  - https://r-pkgs.org/lsicense.html
  - https://thinkr-open.github.io/licensing-r/rlicense.html
  - https://kbroman.org/pkg_primer/pages/licenses.html
- [ ] Get functions to work with multiple and no trns (character(0) and NA) in one element
  - rapply(~ifelse(. == 1,NA,.), how = "replace")
  - purrr::modify_if()
  - any(lengths(y) > 1) # flatten if max 1 trn per element...but issue with character(0)
